Normalization by Evaluation for Call-By-Push-Value and Polarized Lambda Calculus

### 2019-05-10 ppdp19/ppdp19.tex
[ ppdp19 ] link to Agda soundness of NbE for IPL in footnote

%\emph{Normalization}
Normalization is concerned with finding a normal form
$n : \Nf A \Gamma$ for each term $t : A \from \Gamma$.
The normal form should be \emph{sound},
\ie, $\tm n \cong t$
with respect to an equational theory $\cong$ on terms%
. %(see \cref{sec:eq}).
Further, normalization should decide $\cong$, \ie,
terms $t,t'$ with $t \cong t'$ should have the same normal form $n$.
In this article, we implement only the normalization function
\fbox{$\tnorm : A \from \Gamma \to \Nf A \Gamma$}
with proving its soundness and completeness.
From a logical perspective, we will compute for each derivation of $A
\from \Gamma$ a normal derivation $\Nf A \Gamma$.

>>>>

%\emph{Normalization}
Normalization is concerned with finding a normal form
$n : \Nf A \Gamma$ for each term $t : A \from \Gamma$.
The normal form should be \emph{sound},
\ie, $\tm n \cong t$
with respect to an equational theory $\cong$ on terms%
. %(see \cref{sec:eq}).
Further, normalization should decide $\cong$, \ie,
terms $t,t'$ with $t \cong t'$ should have the same normal form $n$.
In this article, we present only the normalization function
\fbox{$\tnorm : A \from \Gamma \to \Nf A \Gamma$}
without proving its soundness and completeness.%
\footnote{An Agda formalization of NbE for IPL with
soundness-by-construction is listed at
  \url{https://andreasabel.github.io/ipl/html/NbeModel.html}.
It is demonstrated that normalization does not change the
interpretation of a term as function in the meta-language.
Instead of presheaves, we work with Kripke predicates there.
The main contribution of our work, the utilization of a cover monad
for NbE, is however more clearly presented by just constructing the
normalization function, as we do in this article.
}
From a logical perspective, we will compute for each derivation of $A
\from \Gamma$ a normal derivation $\Nf A \Gamma$.
